---
title: "R Notebook"
output: html_notebook
---

# Obtaining information between the samples

```{r setup}
library(tidyverse)
library(here)
library("readxl")
library(VennDiagram)
library(eulerr)
library(gridExtra)
library(Biostrings)
```

```{r loading the files}
comparison <- dir(path = ".", pattern = "\\COMPARISON.rds", full.names = FALSE, recursive = TRUE)
ANTI_r <- dir(path = ".", pattern = "\\ANTI_rnaSeq.rds", full.names = FALSE, recursive = TRUE)
ANTI_t <- dir(path = ".", pattern = "\\ANTI_targeted.rds", full.names = FALSE, recursive = TRUE)
```

# Making a venn diagram for each sample to show the number of sequences that overlapped and didn't between RNA_seq and Targeted
```{r}
info_table <- read_excel("info_comparison.xlsx", sheet=1)
info_table
important_data <- cbind(info_table$calculated_start_RNASeq, info_table$start_targeted_IN, info_table$compared)
important_data
file_names  <- cbind(info_table$Sample_RNAseq, info_table$Sample_targeted)
file_names
for (i in 1:20) {
venn.plot <- draw.pairwise.venn(area1      = print(important_data[i,1]),
                                area2      = print(important_data[i,2]),
                                cross.area = print(important_data[i,3]),
                                category   = c(paste(file_names[i,1]),paste(file_names[i,2])),
                          fill=c("darkmagenta", "darkblue"),
                          main = paste(file_names[i,1],paste('vs'),paste(file_names[i,2])))

png(paste(file_names[i,1],paste(file_names[i,2],'diagram.png')));
grid.draw(venn.plot);
dev.off()
}
```

```{r}
# finding the coefficent for the compared number of sequences in comparison to the start number of sequences
lm(data = info_table, compared ~ start_targeted_IN) %>% summary() #0.055182
lm(data = info_table, compared ~ start_rnaSeq) %>% summary() #0.4304
```
```{r}
lm(data = info_table, Anti_targeted ~ start_targeted_IN) %>% summary() #1.1764
lm(data = info_table, Anti_rnaSeq ~ start_rnaSeq) %>% summary() #0.5782
```
```{r}
# Plotting normalised results
ggplot(data= info_table) + aes(x = Percentage_TARGETED, y = Percentage_RNASEQ) + geom_point() # This plots the percentage of the overlapped sequences in RNA_seq against the percentage of the overlapped sequences in targeted
ggplot(data= info_table) + aes(x = normalised_Anti_targeted, y = normalised_Anti_rnaSeq, group) + geom_point() + facet_wrap(~Sample_RNAseq)
```

# Finding the GC content and sequence length within each nCDR3seq in all the samples for overlapped, anti_RNAseq and anti_targeted. 
```{r}
for (i in comparison){
  samplename <- sub("_COMPARISON.rds", "", i)
  haeyam <- readRDS(i)
  haeyam <- haeyam %>%
	mutate(gc_content = letterFrequency(DNAStringSet(nSeqCDR3), "GC", as.prob = TRUE)[,"G|C"]) %>% 
  mutate(width = width(DNAStringSet(nSeqCDR3))) 
haeyam$samplename <- paste0(haeyam$samplename, "_overlap")
haeyam <- select(haeyam, samplename, gc_content,width)
  write_tsv(haeyam, paste((samplename),'summary_OL.tsv'))
}

for (i in ANTI_r){
  samplename <- sub(".ANTI_rnaSeq.rds", "", i)
  haeyam <- readRDS(i)
  haeyam <- haeyam %>%
	mutate(gc_content = letterFrequency(DNAStringSet(nSeqCDR3), "GC", as.prob = TRUE)[,"G|C"]) %>% 
  mutate(width = width(DNAStringSet(nSeqCDR3))) 
haeyam$samplename <- paste0(haeyam$samplename, "_anti_RNAseq")
haeyam <- select(haeyam, samplename, gc_content,width)
  write_tsv(haeyam, paste((samplename),'summary_ANTI_RS_.tsv'))
}

for (i in ANTI_t){
  samplename <- sub(". ANTI_targeted.rds", "", i)
  haeyam <- readRDS(i)
  haeyam <- haeyam %>%
    drop_na() %>% 
	mutate(gc_content = letterFrequency(DNAStringSet(nSeqCDR3), "GC", as.prob = TRUE)[,"G|C"]) %>% 
  mutate(width = width(DNAStringSet(nSeqCDR3))) 
  haeyam$samplename <- samplename
  haeyam$samplename <- paste0(haeyam$samplename, "_anti_Targeted")
  haeyam <- select(haeyam, samplename, gc_content,width)
  write_tsv(haeyam, paste((samplename),'summary_ANTI_T_.tsv'))
}
```
# Plotting box plots
```{r}
concat <- dir(path = ".", pattern = "\\concat.tsv", full.names = FALSE, recursive = TRUE)
for (a in concat){
  samplename <- samplename <- sub("_summary_concat.tsv", "", a)
  f1 <- read_tsv(a)
  box.plot <- boxplot(f1$gc_content~f1$samplename, names=c("anti_RNA_seq", "anti_Targeted", "Overlapped"), xlab= "Sample", ylab= "GC_content", main= samplename)
  png(paste(samplename),'boxplot.png');
grid.draw(box.plot);
dev.off()
}
```

# Experimenting with different versions of boxplots 
```{r}
ggplot(a, aes(x= samplename, y= gc_content, colour= samplename)) + geom_violin() + geom_boxplot(width=0.1) # This shows the density of the each sample. Able to visualise the distribution more clearly to see where there is a high density for GC content.  
ggplot(a, aes(x= samplename, y= gc_content, colour= samplename)) + geom_jitter() + theme(axis.text.x= element_text(angle = 90)) # This plots each nSeqCDR3 as a point, this also shows more clearly where there is a higher amount of sequences for a particular GC content percentage 
```